A performance assessment of evolutionary algorithms in volunteer computing environments: the importance of entropy

### 2016-11-15 EvoPar2017/paper.tex
Couple of comments...

graph2 & 1173561.5 & 6 & 4 & 761.5 & 22.0 & 0.0520509 & 36 & 73 & 129.04545\\
\hline
reboot & 796214.0 & 9 & 6 & 646.0 & 67.0 & 0.0955121 & 45 & 168 & 75.88889\\
\hline
cachereboot & 392917.0 & 12 & 12 & 576.0 & 79.0 & 0.1575092 & 55 & 225 & 43.28571\\
\hline
\end{tabular}
%% \end{tabular}
%% Initially generated with this code, 
% <<experiments, cache=FALSE,echo=FALSE>>=
%experiment.aggregates$Experiment <- c("base","graph1","graph2","reboot","cachereboot")
%kable(experiment.aggregates)
%@ %def 
\end{center}
\end{table}
%
%
%
Since the point of using a volunteer computing system is to cut costs,
all experiments were set up using the OpenShift
PaaS, which provides a free tier, making the whole experiment cost
equal to nil. In fact, the NodIO system can be deployed to any
Platform or Infraestructure as a Service 
system as long as it can run node.js and can store logs on the same
place or in some other Log as a Service. Local storage can be used,
but it is not a requisite and, in fact, Heroku does not allow
persistent storage of files in its service. 
All these logs are available upon
request. Processed files are available in the same repository that
hosts this paper, as well as the scripts needed to process them.

>>>>

graph2 & 1173561.5 & 6 & 4 & 761.5 & 22.0 & 0.0520509 & 36 & 73 & 129.04545\\
\hline
reboot & 796214.0 & 9 & 6 & 646.0 & 67.0 & 0.0955121 & 45 & 168 & 75.88889\\
\hline
cachereboot & 392917.0 & 12 & 12 & 576.0 & 79.0 & 0.1575092 & 55 & 225 & 43.28571\\
\hline
\end{tabular}
%% \end{tabular}
%% Initially generated with this code, 
% <<experiments, cache=FALSE,echo=FALSE>>=
%experiment.aggregates$Experiment <- c("base","graph1","graph2","reboot","cachereboot")
%kable(experiment.aggregates)
%@ %def 
\end{center}
\end{table}
%
%
%
Since the point of using a volunteer computing system is to cut costs, %actually, we talk about the system being efficient, and also the algorithm itself, but I think we don't talk about the costs...
all experiments were set up using the OpenShift
PaaS, which provides a free tier, making the whole experiment cost
equal to nil. In fact, the NodIO system can be deployed to any
Platform or Infrastructure as a Service 
system as long as it can run \texttt{node.js} and can store logs on the same
place or in some other Log as a Service. Local storage can be used,
but it is not a requisite and, in fact, Heroku %first time Heroku is mentioned...
 does not allow
persistent storage of files in its service. 
All these logs are available upon
request. Processed files are available in the same repository that
hosts this paper, as well as the scripts needed to process them.
